### 2022-05-10 supplement.Rmd

>>>>

```{r, trim_and_fill_within}

# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# run trim and fill
res_tf <- trimfill(r_mod)
print(res_tf)
res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"

summ_brm <- list(intercept = res_tf$beta)
# Compute funnel
funnel_z_crit <- stats::qnorm(0.975)
funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
funnel <- data.frame(
  x = c(
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
  ),
  y = c(funnel_max_se, 0, 0, funnel_max_se)
)

# # Create funnel plot
plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
  # Meta-analytic effect size
  geom_vline(xintercept = summ_brm$intercept, color = "black") +
  # Experiment-specific effect sizes
  geom_point(shape = 0) +
  # Funnel
  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
  # Styling
  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
  scale_y_reverse() +
  coord_cartesian(
    xlim = c(-2.5, 2.5),
    ylim = c(funnel_max_se, 0),
    expand = FALSE
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    y = "Standard error",
  ) +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(family = "Helvetica", color = "black")
  )

# Save the plot
ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
```

```{r,selection_models_within}
# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# EASY WEIGHT_FUNCTION MODEL
# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
# to estimate the population effect size after adjusting for selection bias."
# specifying p value cutpoints of 0.01, 0.05, and 0.10
sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
print(sel_mod)
print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')

# 4 DIFFERENT STEP FUNCTION MODELS
# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that 
# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
tab <- data.frame(
  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))

sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)

print(sel_moderateonetailed)
print(sel_severeonetailed)
print(sel_moderatetwotailed)
print(sel_severetwotailed)

print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')

interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"

```

```{r, tabs_trimfill_selectionmodels_within, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Two-level random effects model",
    "Trim-and-fill",
    "Selection model: weight-function [0.01, 0.05, 0.3]",
    "Selection model: moderate one-tailed",
    "Selection model: severe one-tailed",
    "Selection model: moderate two-tailed",
  "Selection model: severe two-tailed"
  ),
    list(
      r_mod,
      res_tf,
      sel_mod,
      sel_moderateonetailed,
      sel_severeonetailed,
      sel_moderatetwotailed,
      sel_severetwotailed
      ),
  function(name, res) {
    print(name)
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      bind_rows()
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

# Display the table
apa_table(
  tab_freq,
  align = "llccccc",
  caption = "Sensitivity/robustness analyses frequentist",
  font_size = "scriptsize",
  escape = FALSE
)

# Save the table
write_csv(tab_freq, file = here(tables_dir, "robustness_freq.csv"))
```

```{r, trim_and_fill_gender}
dat=dat_gender

# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# run trim and fill
res_tf <- trimfill(r_mod)
print(res_tf)
# res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"

summ_brm <- list(intercept = res_tf$beta)
# Compute funnel
funnel_z_crit <- stats::qnorm(0.975)
funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
funnel <- data.frame(
  x = c(
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
  ),
  y = c(funnel_max_se, 0, 0, funnel_max_se)
)

# # Create funnel plot
plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
  # Meta-analytic effect size
  geom_vline(xintercept = summ_brm$intercept, color = "black") +
  # Experiment-specific effect sizes
  geom_point(shape = 0) +
  # Funnel
  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
  # Styling
  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
  scale_y_reverse() +
  coord_cartesian(
    xlim = c(-2.5, 2.5),
    ylim = c(funnel_max_se, 0),
    expand = FALSE
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    y = "Standard error",
  ) +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(family = "Helvetica", color = "black")
  )

# Save the plot
ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
```

```{r,selection_models_gender}
# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# EASY WEIGHT_FUNCTION MODEL
# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
# to estimate the population effect size after adjusting for selection bias."
# specifying p value cutpoints of 0.01, 0.05, and 0.10
sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
print(sel_mod)
# print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')

# 4 DIFFERENT STEP FUNCTION MODELS
# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that 
# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
tab <- data.frame(
  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))

sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)

print(sel_moderateonetailed)
print(sel_severeonetailed)
print(sel_moderatetwotailed)
print(sel_severetwotailed)

# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
# print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
# print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')

# interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"

```

```{r, tabs_trimfill_selectionmodels_gender, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Two-level random effects model",
    "Trim-and-fill",
    "Selection model: weight-function [0.01, 0.05, 0.3]",
    "Selection model: moderate one-tailed",
    "Selection model: severe one-tailed",
    "Selection model: moderate two-tailed",
  "Selection model: severe two-tailed"
  ),
    list(
      r_mod,
      res_tf,
      sel_mod,
      sel_moderateonetailed,
      sel_severeonetailed,
      sel_moderatetwotailed,
      sel_severetwotailed
      ),
  function(name, res) {
    print(name)
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      bind_rows()
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

# Display the table
apa_table(
  tab_freq,
  align = "llccccc",
  caption = "Sensitivity/robustness analyses frequentist",
  font_size = "scriptsize",
  escape = FALSE
)

# Save the table
write_csv(tab_freq, file = here(tables_dir, "robustness_freq_gender.csv"))
```
